The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-11-08 outputs/docs/events/paper.Rmd
Update paper
Add appendix about choosing topic number

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)"
thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, and the Parliamentary Library. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: changes in government tend be associated with topic changes even when the party in power does not change; elections that do not result in a change in government are rarely associated with topic changes; economic events, such as financial crises, have less significant effects than other events such as terrorist attacks; and the effect of events is much more pronounced in the second half of our sample, and especially in the past two decades. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
keywords: "text, politics, Australia, unsupervised machine learning, Bayesian model."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis. This literature sits across and draws from various historically-separate disciplines including economic history, political science, and applied statistics. We contribute to this literature in terms of both data and methods. To the best of our knowledge we are the first to bring to bear an essentially-complete record of what was said in the Australian Federal Parliament, and we make our dataset available to other researchers via the R package \texttt{hansardr}. From a methods perspective, our analysis model has several advantages over existing methods. These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest. As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.

@@

Parts of Australian Hansard records have been analysed for various purposes. For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment. @FraussenGrahamHalpin2019 examined Australian Hansard records to assess the prominence of interest groups. The closest research to ours that we have found is @Boulous2013 who examines parliamentary debate in Australia for the period 1946 to 2012.

@@

The goal of our modelling strategy is twofold. Firstly, we want to use topic modelling [@Blei2003latent] to summarise the Hansard text into meaningful topics that reduce the dimensionality of the text data and capture the main themes discussed in parliament over time. Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in government, elections, and other external events.

We use the Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time. We consider these topic distributions as reduced dimension inputs that can be analysed within another model. We then formulate a Bayesian hierarchical Dirichlet model to assess changes in the topic distributions in relation to events of interest.

In the following sections, we describe both the topic modelling approach and the Bayesian hierarchical analysis model. Firstly, we describe the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before moving onto the CTM, which is a natural extension of LDA. We then discuss the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics.

@@

@@

There are a variety of diagnostic measures that can guide the selection of the topics, but there is rarely an obvious best choice and we found it useful to try a few quite different measures before settling on 80 topics. Useful diagnostic measures that we considered include the held-out likelihood, the lower bound, residuals, and semantic coherence (Figures \@ref(fig:topicsdiagnostics)).[^Silgefootnote]

@@

**[Discuss each of these...]**

Additionally, the tradeoff between exclusitivity and semantic coherence...  (Figure \@ref(fig:topicsexclusivityvscoherence))

@@

**[Discuss this one too...]**

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)"
thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, and the Parliamentary Library. Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to elections and changed governments in Australian history. We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: changes in government tend be associated with topic changes even when the party in power does not change; elections that do not result in a change in government are rarely associated with topic changes; economic events, such as financial crises, have less significant effects than other events such as terrorist attacks; and the effect of events is much more pronounced in the second half of our sample, and especially in the past two decades. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
keywords: "text, politics, Australia, unsupervised machine learning, Bayesian model."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis. This literature sits across and draws from various historically-separate disciplines including economic history, political science, and applied statistics. We contribute to this literature in terms of both data and methods. From a data perspective we bring to bear an essentially-complete record of what was said in the Australian Federal Parliament, and we make our dataset available to other researchers via the R package \texttt{hansardr}. From a methods perspective, our analysis model has several advantages over existing methods. These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest. As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.

@@

Parts of Australian Hansard records have been analysed for various purposes. For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment. And @Salisbury2011 examines unparliamentary behaviour. @FraussenGrahamHalpin2019 examined Australian Hansard records to assess the prominence of interest groups. The closest research to ours that we have found is @Boulous2013 who examines parliamentary debate in Australia for the period 1946 to 2012.

@@

The goal of our modelling strategy is twofold. Firstly, we want to use topic modelling [@Blei2003latent] to summarise the Hansard text into meaningful topics that reduce the dimensionality of the text data and capture the main themes discussed in parliament over time. Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in government, elections, and other external events. There are two stages in our analytical process.

We first use the Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time. We consider these topic distributions as reduced dimension inputs that can be analysed within another model. We then formulate a Bayesian hierarchical Dirichlet model to assess changes in the topic distributions in relation to events of interest.

In the following section, we briefly describe the topic modelling approach, which is to use the CTM, which is a natural extension of the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before discussing the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics. More detail on the topic modelling is available for readers that may be less familiar with it in Appendix \@ref(hansardworkflow)

@@

In the Senate, the PDF for 10 August 1917 may be the wrong one? It says it is for 10 Jan 1918 on the cover sheet, but there's not even an entry for 10 Jan 1918...??? Very odd....

Senate Hansard - 1918-12-18 has the wrong PDF so does 1917-08-01.

@@

There are a variety of diagnostic measures that can guide the selection of the topics, but there is rarely an obvious best choice, especially at a more fine level such as choosing betweeen 60 and 65 topics. We found it useful to try a few quite different measures before settling on 80 topics. This provided a balance between being granular enough to be informative--anything less than 40 topics tended to be too broad-- yet still being tractable for our analysis model in a reasonable amount of time. In addition to looking at the topics and how they changed over time, diagnostic measures that we considered include the held-out likelihood, the lower bound, residuals, exclusivity. and semantic coherence (Figures \@ref(fig:topicsdiagnostics)).[^Silgefootnote]

@@

@RobertsStewartAiroldiRPackage provides more detail about the diagnostic tests that we use, but we briefly discuss each here. Exclusivity is a measure of how specific words are to particular topics. It looks at the proportion that a word makes up of a particular topic compared with the proportion that word makes up of the other topics. As the number of topics increases we usually expect exclusivity to increase because the topics become more particular. Higher values are better. The held out likelihood as described by @Wallach2009 takes a test/training approach to estimate the probability of held-out documents given the training documents. Higher values are better. The lower bound gives some indication of whether the model may have multiple modes and hence the end result be sensitive to the starting position (@Roberts2016navigating). Residuals analysis (@Taddy2012) compares the theoretical distribution of the variance with the eactual distribution. It is a test for overdispersion of the variance, and if it is found then this can suggest that more topics would be appropriate. Semantic coherence is the tradeoff for having topics that are more specific and the subsequent risk that the topics become meaningless. @Mimno2011 define a measure of coherence that is based on ratios of single words compared with pairs of words. The idea is that words that should occur in the one document should be more likely to be in a particular topic than ones that do not occur together. For instance, a topic that has 'wine' and 'cheese' as highly rated words would score better on their measure than another that contained 'cheese' and 'mining'. Lower values are better. @RobertsStewartAiroldiRPackage recommend examining the tradeoff between exclusitivity and semantic coherence. This suggests that the magnitude of improvement reduces from about 80 topics (Figure \@ref(fig:topicsexclusivityvscoherence)).

@@
